Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-03-28 DGMM2025/paper.tex
citation fix
statement visibility not 26-connected

    We recall essential definitions from previous works, particularly the notions of , cell complexes, and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
    A cell complex is a decomposition of space into elementary units—vertices, edges, faces, and higher-dimensional counterparts—forming a combinatorial representation of geometric objects.
    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.

@@

    The remainder of this paper is structured as follows.
    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite*{lachaud:2022-dcg}.
    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.

@@

    Introduce full convexity and tangency. \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}.

@@

>>>>

    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
    A cell complex is a decomposition of space into elementary units—vertices, edges, faces, and higher-dimensional counterparts—forming a combinatorial representation of geometric objects.
    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.

@@

    The remainder of this paper is structured as follows.
    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite{lachaud:2022-dcg}.
    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.

@@

@@

    We note that one particular aspect of this visibility definition is that all visible points from a given point taken as a separate complex are not necessarily 26-connected~\ref{fig:visibility-2d-not-connected}.
    Furthermore, we conjecture that they even may not be $n$-connected for $n$ arbitrarily large.
    This characteristic has implications for the applicability of Algorithm 3 from~\cite{lachaud:2022-jmiv}, as the algorithm assumes that visited points are 26-connected, potentially leading to incomplete collection of visible points.
